The Recursive Bernstein-Vazirani Algorithm

### 2018-06-04 Quantum Computation/rBV/rBernsteinVazirani.tex
add html ver converted from latex by lwarp (experimental)

% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
\usepackage[log-declarations=false]{xparse}
\usepackage[final]{physicist-taper}

@@

Here the $H^{\otimes n}_j$ is simply the $n$ bit Hadamard gate $H^{\otimes n}$ acting
on the $j$th register. Each operator $D_{k-j}$ solve the $j$th level rBV
problem. Specifically, the first operator $D_k$ does the following:
\begin{align}
  & D_k \sum_{\vec{x}_1,\cdots,\vec{x}_k} \ket{\vec{x}_1,\cdots,\vec{x}_k}\nonumber\\ 
  = & H^{\otimes n}_k \sum_{\vec{x}_1,\cdots,\vec{x}_k}
  (-1)^{\vec{x}_k\vdot\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}} 
  \ket{\vec{x}_1,\cdots,\vec{x}_k} \\
  = & H_k^{\otimes n} \sum_{\vec{x}_1,\cdots,\vec{x}_{k-1}}
  \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},P_{\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}}}
  \\
  = & \sum_{\vec{x}_1,\cdots,\vec{x}_{k-1}}
  \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}}.
\end{align}
Notice that if there are some arbitrary non-zero phases
$\phi(\vec{x}_1,\cdots,\vec{x}_k)$ in front of
$\ket{\vec{x}_1,\cdots,\vec{x}_k}$ on the first line, the final result will not
change except from this arbitrary phase. $D_k$ can be understood as the following
diagram:
\begin{equation}
\begin{tikzcd}
  \ket{\cdots,\vec{x}_k} \arrow[r, bend left, "D_k"] & 
   \arrow[l, bend left, "D^\dagger_k"] 
   \ket{\cdots,\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}}.
\end{tikzcd}
\end{equation}

@@

Similarly, we have the following diagram for $D_{k-1}$:
\begin{equation}
\begin{tikzcd}
  \ket{\cdots,\vec{x}_{k-1},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}} 
  \arrow[r, "\text{load phase}", "g_{k-1}" below,]
  \dar[bend left, "D_{k-1}"]
  & 
  (-1)^{\cdots} \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}}
  \dar["D^\dagger_k"]
  \\
  \ket{\cdots,\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-2}},P_0}
  \uar[bend left, "D^\dagger_{k-1}"]
  &
  (-1)^{\cdots} \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{x}_{k}}
  \lar["\text{unload phase}" above, "H"]
\end{tikzcd}
\end{equation}

@@

\begin{equation}
\begin{tikzcd}[row sep=large, column sep = large]
  \ket{\cdots,\vec{x}_{k-j},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j}},P_0^{\otimes j-1}} 
  \arrow[r, "\text{load phase}", "g_j" below,]
  \dar[bend left, "D_{k-j}"]
  & 
  (-1)^{\cdots} 
  \ket{\cdots,\vec{x}_{k-j},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j}},P_0^{\otimes j-1}} 
  \dar["D^\dagger_k\cdots D^\dagger_{k-j+1}"]
  \\
  \ket{\cdots,\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j-1}},P_0,P_0^{\otimes j-1}}
  \uar[bend left, "D^\dagger_{k-j}"]
  &
  (-1)^{\cdots} \ket{\vec{x}_1,\cdots,\vec{x}_{k-j}, \vec{x}_{k-j+1},\cdots,\vec{x}_{k}}
  \lar["\text{unload phase}" above, "H"]
\end{tikzcd}
\end{equation}

The operators $D^\dagger_k\cdots D^\dagger_{k-j+1}$ solves the lower level
problem by gradually moving the $s$ number to the end:
\begin{equation}
\begin{tikzcd}
  \ket{\cdots,\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j}},P_0,P_0^{\otimes j-2}}
  \rar["D^\dagger_{k-j+1}"]
  &
  \ket{\cdots,\vec{x}_{k-j+1}, \vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j+1}},P_0^{\otimes j-2}}
  \dar["\cdots"]
  \\
  \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{x}_{k}}
  &
  \ket{\cdots,\vec{x}_{k-j+1},\cdots,\vec{x}_{k-1},\vec{s}_{\vec{x}_{k-1}}}
  \lar["D_k"]
\end{tikzcd}
\end{equation}

>>>>

% for lwarp package: converting latex to html.
\usepackage{iftex}

% --- LOAD FONT SELECTION AND ENCODING BEFORE LOADING LWARP ---

\ifPDFTeX
\usepackage{lmodern}            % pdflatex
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\else
\usepackage{fontspec}           % XeLaTeX or LuaLaTeX
\fi

% --- LWARP IS LOADED NEXT ---
\usepackage[
%   latexmk,                    % Use latexmk to compile.
%   mathjax,                    % Use MathJax to display math.
]{lwarp}

% --- LATEX AND HTML CUSTOMIZATION ---
\setcounter{tocdepth}{2}        % Include subsections in the \TOC.
\setcounter{secnumdepth}{2}     % Number down to subsections.
\setcounter{FileDepth}{-5}       % To place the entire file into one html page
\booltrue{CombineHigherDepths}  % Combine parts/chapters/sections
\setcounter{SideTOCDepth}{1}    % Include subsections in the side\TOC
\HTMLLanguage{en-UK}            % Sets the HTML meta language.
\CSSFilename{lwarp_formal.css}

% --- OTHER PACKAGES ARE LOADED AFTER LWARP ---
% My own physics package
% The following line load the package xparse with additional option to
% prevent the annoying warnings, which are caused by the package
% "physics" loaded in package "physicist-taper".
% \usepackage[log-declarations=false]{xparse}
\usepackage[final]{physicist-taper}

% for lwarp to work with tikz
\tikzset{every picture/.style={ampersand replacement=\&}}

@@

Here the $H^{\otimes n}_j$ is simply the $n$ bit Hadamard gate $H^{\otimes n}$ acting
on the $j$th register. Each operator $D_{k-j}$ solve the $j$th level rBV
problem. Specifically, the first operator $D_k$ does the following:
\begin{align}
  & D_k \sum_{\vec{x}_1,\cdots,\vec{x}_k} \ket{\vec{x}_1,\cdots,\vec{x}_k}\nonumber\\ 
  = & H^{\otimes n}_k \sum_{\vec{x}_1,\cdots,\vec{x}_k}
  (-1)^{\vec{x}_k\vdot\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}} 
  \ket{\vec{x}_1,\cdots,\vec{x}_k} \\
  = & H_k^{\otimes n} \sum_{\vec{x}_1,\cdots,\vec{x}_{k-1}}
  \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},P_{\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}}}
  \\
  = & \sum_{\vec{x}_1,\cdots,\vec{x}_{k-1}}
  \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}}.
\end{align}

Notice that if there are some arbitrary non-zero phases
$\phi(\vec{x}_1,\cdots,\vec{x}_k)$ in front of
$\ket{\vec{x}_1,\cdots,\vec{x}_k}$ on the first line, the final result will not
change except from this arbitrary phase. $D_k$ can be understood as the following
diagram:
\displaymathother
\begin{equation}
\begin{tikzcd}
  \ket{\cdots,\vec{x}_k} \arrow[r, bend left, "D_k"] \& 
   \arrow[l, bend left, "D^\dagger_k"] 
   \ket{\cdots,\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}}.
\end{tikzcd}
\end{equation}
\displaymathnormal

@@

Similarly, we have the following diagram for $D_{k-1}$:
\displaymathnormal
\begin{equation}
\begin{tikzcd}
  \ket{\cdots,\vec{x}_{k-1},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}} 
  \arrow[r, "\text{load phase}", "g_{k-1}" below,]
  \dar[bend left, "D_{k-1}"]
  \& 
  (-1)^{\cdots} \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-1}}}
  \dar["D^\dagger_k"]
  \\
  \ket{\cdots,\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-2}},P_0}
  \uar[bend left, "D^\dagger_{k-1}"]
  \&
  (-1)^{\cdots} \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{x}_{k}}
  \lar["\text{unload phase}" above, "H"]
\end{tikzcd}
\end{equation}
\displaymathother

@@

\displaymathother
\begin{equation}
\begin{tikzcd}[row sep=large, column sep = large]
  \ket{\cdots,\vec{x}_{k-j},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j}},P_0^{\otimes j-1}} 
  \arrow[r, "\text{load phase}", "g_j" below,]
  \dar[bend left, "D_{k-j}"]
  \& 
  (-1)^{\cdots} 
  \ket{\cdots,\vec{x}_{k-j},\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j}},P_0^{\otimes j-1}} 
  \dar["D^\dagger_k\cdots D^\dagger_{k-j+1}"]
  \\
  \ket{\cdots,\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j-1}},P_0,P_0^{\otimes j-1}}
  \uar[bend left, "D^\dagger_{k-j}"]
  \&
  (-1)^{\cdots} \ket{\vec{x}_1,\cdots,\vec{x}_{k-j}, \vec{x}_{k-j+1},\cdots,\vec{x}_{k}}
  \lar["\text{unload phase}" above, "H"]
\end{tikzcd}
\end{equation}
\displaymathnormal

The operators $D^\dagger_k\cdots D^\dagger_{k-j+1}$ solves the lower level
problem by gradually moving the $s$ number to the end:
\displaymathother
\begin{equation}
\begin{tikzcd}
  \ket{\cdots,\vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j}},P_0,P_0^{\otimes j-2}}
  \rar["D^\dagger_{k-j+1}"]
  \&
  \ket{\cdots,\vec{x}_{k-j+1}, \vec{s}_{\vec{x}_1,\cdots,\vec{x}_{k-j+1}},P_0^{\otimes j-2}}
  \dar["\cdots"]
  \\
  \ket{\vec{x}_1,\cdots,\vec{x}_{k-1},\vec{x}_{k}}
  \&
  \ket{\cdots,\vec{x}_{k-j+1},\cdots,\vec{x}_{k-1},\vec{s}_{\vec{x}_{k-1}}}
  \lar["D_k"]
\end{tikzcd}
\end{equation}
\displaymathnormal
